---
title: "BiocKubeInstall Usage"
author:
- name: Nitesh Turaga
  affiliation: Dana Farber Cancer Institute
package: BiocKubeInstall
output:
  BiocStyle::html_document
abstract: |
  The BiocKubeInstall package is a cloud computing resource meant to be
  used with Kubernetes. The package is used to create binaries for
  R and Bioconductor packages on specific docker images created by
  Bioconductor. It works in concert with k8sredis - the Kubernetes
  application and RedisParam package that parallelizes over a
  Kubernetes cluster. The package requires knowledge of the google
  cloud, kubernetes, and binary package creation. It is an internal
  package to Bioconductor used to make creation and  maintainence
  of package binaries easier and faster.
vignette: |
  %\VignetteIndexEntry{BiocKubeInstall Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Prerequesites

The following steps assume you have a Google cloud account, kubernetes
controller (`kubectl`) installed, and your Google account configured,
and have the following APIs enabled on the project at a minimum.

	- Kubernetes Engine Admin
	- Storage Admin
	- Service account Admin

These services cost money, and are to be used at your expense.

# Kubernetes setup

The 'BiocKubeInstall' package uses the `k8sredis` kubernetes
configuration files to apply the kuberenetes configurations on to the
GKE cluster.

Once you have `k8sredis` downloaded from
https://github.com/Bioconductor/k8sredis, you can do the following.

### Steps:

Default settings used in the following commands are based on local
preferences. Please change them according to your needs.

**cluster name**: biock8scluster

**zone**: us-east1-b

**service account name**: bioc-binaries

**project ID**: fancy-house-303821

1. Start a kubernetes cluster,

		gcloud container clusters create \
			--zone us-east1-b \
			--num-nodes=6 \
			--machine-type=e2-standard-4 biock8scluster

1. Get the cluster credentials on your local machine,

		gcloud container clusters get-credentials --zone us-east1-b biock8scluster

1. Create a service account key. The service account key has 'Storage
   Admin' permissions, so it can upload the binaries to a google
   bucket.

		## Create service account
		gcloud iam service-accounts create bioc-binaries \
			--display-name "Storage Admin SA" \
			--description "Bioc Binaries storage admin"

		## List service account
		gcloud iam service-accounts list \
			--filter bioc-binaries@fancy-house-303821.iam.gserviceaccount.com

		## Download service account key locally
		gcloud iam service-accounts keys create \
			bioc-binaries.json \
			--iam-account bioc-binaries@fancy-house-303821.iam.gserviceaccount.com

		## Add 'Storage Admin' role to service account.
		gcloud projects add-iam-policy-binding fancy-house-303821 \
			--member \
			"serviceAccount:bioc-binaries@fancy-house-303821.iam.gserviceaccount.com" \
			--role "roles/storage.admin"

1. Start NFS volume which is going to be attached to your
   k8s compute nodes. The NFS mount is where the binary packages will
   be stored. The location of the NFS volume is under the directory
   `/host` on your compute nodes.

		kubectl apply -f k8s/nfs-volume/

1. Create a kubernetes secret from the service account key which was
   downloaded in the previous steps `bioc-binaries.json`.

   The service account key is going to be transmitted to the
   kubernetes cluster in an encrypted manner. This command below
   assumes that `bioc-binaries.json` is located in the same path where
   you are running the `kubectl` commands.

		kubectl create secret generic \
			bioc-binaries-service-account-auth \
			--from-file=service_account_key=bioc-binaries.json

1. Once the key is created, you can now launch the `bioc-redis`
   configuration on your kubernetes cluster.

		kubectl apply -f k8s/bioc-redis


### Manage kubernetes cluster (if needed)


A few commands which help with the management of the kubernetes cluster are:

- Check if all the pods, services, and nodes are working as expected:

		kubectl get all

- Describe specific pods or nodes, to check for failures

		kubectl describe pod/manager

- Log into a specific pod,

		kubectl exec pod/manager --stdin --tty /bin/bash

To delete and destroy your kubernetes cluster safely,

	## Stop redis, rstudio services
	kubectl delete -f k8s/bioc-redis/

	## Delete NFS volume (this is not recommended)
	kubectl delete -f k8s/nfs-volume/

	## Delete the kubernetes cluster completely losing all data.
	gcloud container clusters delete biock8scluster


# BiocKubeInstall

## Introduction


## Cluster architecture and design

The k8s application launches multiple pods on the nodes within the
cluster. The pods are classified into two types, a single "manager"
pod and multiple "worker" pods. The manager pod delegates
reponsibility i.e the jobs are sent to the workers that actually
perform the task. The worker pods are always listening to the manager
and waiting for a job. Each worker performs a single job till it is
done.

The manager and the worker pass messages between each other using
"redis", and the redis work is available inside the package
"RedisParam".

Storage is also built into the k8s application. The manager and the
worker also share a volume mount on the k8s cluster in the form of an
NFS volume. The volume is mounted on the path `/host/`.

The "jobs" here refer to the building of binary R/Bioconductor
packages. Each pod gets a single job, where the job is to build a
single package binary.

## Run

To run an actual job, there is one relevant function, i.e
`BiocKubeInstall::kube_run()`.

The function needs to be used within the
`k8sredis/k8s/bioc-redis/manager-pod.yaml` file in your `k8sredis` k8s
application. Within the specification of the manager-pod.yaml,

The function takes in the following arguments, the `version` of
Bioconductor, the docker `image_name` for which the binaries are being
built and the number of workers which need to run in parallel as
`worker_pool_size`.

```
args: ["-e", "BiocKubeInstall::kube_run(version = '3.13',
					image_name = 'bioconductor_docker',
					worker_pool_size = 17)"]
```

The docker image of the manager node is always going to be
`bioconductor/bioc-redis:devel`


## Usage of Binaries on `bioconductor_docker` images

```
BiocManager::install('Bioconductor/AnVIL')

AnVIL::install('BiocParallel')
```


## Usage of Binaries on the AnVIL

```{r}
library(AnVIL)

BiocManager::install('Bioconductor/AnVIL')

AnVIL::install('<package_name>')
```


```{r}
sessionInfo()
```
